### 2018-10-01 ms.tex
Small edits to discussion.

We used held-out prevalence point-surveys to measure how well model were predicting the within-polygon, pixel-level malaria risk.
Given the poor performance by all models including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and PseudoSenegal these results must be interpreted with care.
% Add sample size, comparisons etc.
In particular, nearly all of the prevalence point-surveys in PseudoSenegal found zero malaria infections (though the age standardisation moves these to slightly non-zero values).
Given the poor performance of the points-only model, it is not useful to interpret these results as a direct measure of a models ability to predict within-polygon, pixel level risk.
Instead we can, with care, interpret the relative performance of models.
In five cases, the polygon-only and joint model had the same predictive performance on the prevalence point-surveys.
In only one cases, the joint model was marginally better.
Therefore we have no evidence that the joint model is better than the polygon-only model at predicting within-polygon, pixel-level malaria risk.

>>>>

We used held-out prevalence point-surveys to measure how well the models predicted within-polygon, pixel-level malaria risk.
Given the poor performance by all models, including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and PseudoSenegal these results must be interpreted with care.
% Add sample size, comparisons etc.
In particular, a majority of the prevalence point-surveys in all countries found zero malaria infections (though the age standardisation moves these to slightly non-zero values) and small sample sizes were common in the Senegal and Indonesia data.
Given the poor performance of the points-only model, it is not useful to interpret these results as a direct measure of a models ability to predict within-polygon, pixel level risk.
Instead we can, with care, interpret the relative performance of models.
In five cases, the polygon-only and joint model had the same predictive performance on the prevalence point-surveys.
In only one cases, the joint model was marginally better.
Therefore we have no evidence that the joint model is better than the polygon-only model at predicting within-polygon, pixel-level malaria risk.
